Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-01-22 draft.tex
Corrections after discussion with Fred

For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokpill} for details
on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
large total angular momentum $j$; only its third component is restricted to $m = -1,0,+1$.
It is then usual to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
the angular observables dependent on the remaining helicity angle $\theta_2$.
We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
and as defined in \refapp{partial-waves} \fred{A lot of mixing between appendices C and E}, the expansion reads
\begin{equation}
    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,|m|}} S_{k,j}(\vec{\nu}) p_{j}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
\end{equation}
where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
example we have (cf. also \refapp{btokpill})
\begin{equation}
    |m| = \begin{cases}
        0\,, & k = 1,2,6\,\\
        1\,, & k = 3,4,5,7,8,9\,,
    \end{cases}\,.
\end{equation}
The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
have the merit of a well defined total angular momentum, and thus are physically discriminable.
As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
ignoring further (orthogonal) terms in the PDF cannot affect the mean vector $(\dots, S_k, \dots)$ nor its variance. \fred{yes!}\\

@@

In order to finally extract the angular observables from data, we use the \emph{measured raw moments}. Their MC estimator
$\lbrace \est{Q}_i\rbrace$ -- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ -- reads
\begin{equation}
    \est{Q}_i \equiv R \frac{1}{N} \sum_n^N \tilde{f}_i(x^{(n)})\,.
\end{equation}
Here $R \equiv \int P(x) \eps(x)$ is an a priori unknown normalization that also occurs in the determination of the branching
ratio of the specific decay. We then obtain MC estimators of the angular observables via
\begin{equation}
    \est{S}_i \equiv \sum_{i} \left(\hat{M}^{-1}\right)_{ij} \est{Q}_j\,.
\end{equation}
The precise value of $R$ depends on the a priori unknown angular observables $\lbrace S_i\rbrace$.
However, ratios and other suitable combinations of the estimators $\lbrace \est{S}_i\rbrace$ are independent
of $R$.

It remains to be emphasized that the dimensionality of the raw angular observables is not completely
fixed by the number of angular momentum configurations of the process at hand. Let us revisit the
decay $B\to K\ell^+\ell^-$, with only one angle,  to clear this up. For $B\to K\ell^+\ell^-$, the
total angular momentum associated the dilepton pair can, at the level of observables, be either $0$,
$1$ or $2$. We assume now that the acceptance function $\eps$ can be conveniently expanded in terms
of Legendre polynomials up to maximal angular momentum $L$. From angular momentum conservation
follows immediately that $\dim Q = L + 2$, and thus the unfolding matrix $M$ will be of
dimension $L + 2 \times L + 2$. (For a multiangular distribution the maximum angular momentum
has to be determined in the same way for each angle.)
Since the $\eps$ depends highly on the nature of the particle detector at hand, it remains for
the experimental collaborations to determine the maximum order of such an expansion.

@@

The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts --- reads \cite{Boeer:2014xx}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \sum_i S_i f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and
$N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
The index $i$ should be interpreted as a multi-index, $i \equiv (l_1, l_2, m)$,
where $0 \leq l_1 \leq 2$ and $0 \leq l_2 \leq 1$ denote the total angular momentum in the
dilepton and the $N\pi$ system, respectively, and $-1 \leq m \leq 1$
is the third component of either of the angular momenta.
Our choice of an orthonormal basis and its dual reads
\begin{equation}
\label{eq:lambdab:bases}
\begin{aligned}
    f_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
    & = \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}} p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
    & \times \begin{cases}
            \cos(|m|\theta_3) & m > 0\\
            \sin(|m|\theta_3) & m < 0\\
            1                 & m = 0
        \end{cases}\,,\\
    \tilde{f}_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
    & = \frac{(2l_1 + 1)(2l_2 + 1)}{8\pi}\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}} p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
    & \times \begin{cases}
            2 \cos(|m|\theta_3) & m > 0\\
            2 \sin(|m|\theta_3) & m < 0\\
            1                   & m = 0
        \end{cases}\,.\\
\end{aligned}
\end{equation}
The correspondence between out choice of angular observables in the angular momentum basis, and the angular
observables as defined in reference \cite{Boeer:2014xx} reads
\begin{equation}
\begin{aligned}
    8\pi S_{0, 0,  0} & = 1\,,                                                             &
    8\pi S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,            &
    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
                 &                                                                    &
    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
                 &                                                                    &
    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
where the decay width is
\begin{equation}
    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}\,.
\end{equation}

@@

For the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| < 1$.
The recipe's generating PDFs are therefore
\begin{equation}
    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}\left(\delta_{i,(0,0,0)} + \delta_{i,j}\right)\,,
\end{equation}
where $j$ ís now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.

@@

    8\pi S_{1, 2, +1} & = \frac{4 \sqrt{3} J_{5i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,

@@

    8\pi S_{1, 2, -1} & = \frac{6 J_{?}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                      &
    8\pi S_{1, 2, -1} & = \frac{4 \sqrt{3} J_{?}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                             \\

@@

    8\pi S_{2, 0,  0} & = \frac{4 (J_{2c} + 2 J_{2s})}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                        &

@@

    8\pi S_{2, 2,  0} & = \frac{8 (J_{2c} - J_{2s})}{3 \rmdx{\Gamma}/\rmdx{q^2}}\,,                        \\

@@

As before, for the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| \leq 1$.
The recipe's generating PDFs are therefore
\begin{equation}
    P(x|\lbrace S_k^{(j)}\rbrace)\,,\quad\text{with}\quad S_k^{(j)} = \frac{1}{8\pi}\left(\delta_{k,0} + \delta_{k,j}\right)\,,
\end{equation}
where also $j$ is now a multi-index representing $j \sim (l_1, l_2, m)$.

@@

We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
\begin{equation}
    S(\theta) = \sum_j S_{j,m} p_{j}^{(m)}(\cos\theta)\,.
\end{equation}
This parametrization has two merits. First, we can immediately project out the angular observables $S_{j,m}$ by means of \refeq{legendre-scalar-product}:
\begin{equation}
    S_{j,m} = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} S(\theta) p_{j}^{(m)}(\cos\theta)\,.
\end{equation}
(Here and in the next step we may exchange the integral and the
series because each element of the series is a product of
polynomials on the compact support [-1,1], and thus each integral
is absolutely convergent).
Second, we can immediately express $S_{j,m}$ in terms of
the partial-wave amplitudes,
\begin{equation}
    \label{eq:partial-wave-observable-infinite}
    \begin{aligned}
        S_{j,m}
            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
            & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{l_1} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
    \end{aligned}
\end{equation}

>>>>

For the selected class of decays, we can describe that problem as follows: The PDF $P$ has a fixed dependence on the dilepton
helicity angle $\theta_1$ and the azimuthal angle $\theta_3$. (See also \refapp{btokstarll} for details
on the angular distribution.) However, at the level of decay amplitudes the dimeson system can have an arbitrarily
large total angular momentum $j$; only its third component is restricted to $j_z = -1,0,+1$.
It is then usual to compute the angular distribution explicitly in terms of $\theta_1$ and $\theta_3$, but leave
the angular observables dependent on the remaining helicity angle $\theta_2$.
We advocate here that is a sensible procedure to perform an expansion in terms of Legendre polynomials $p_{j}^{(|m|)}$
with respect to the remaining angle $\theta_2$. Using the observables $S_k(\vec{\nu})$, $k=1,\dots,9$, with $\vec{\nu}=(q^2, k^2)$
and as defined in \refapp{partial-waves} \fred{A lot of mixing between appendices C and E}, the expansion reads
\begin{equation}
    S_{k}(\vec{\nu},\cos\theta_2) \equiv \sum_{j} \frac{1}{n_{j,|m|}} S_{k,j}(\vec{\nu}) p_{j}^{(|m|)}(\cos\theta_2)\sin\theta_2\,,
\end{equation}
where the the normalization factor $n_{j,|m|}$ is defined in \refeq{legendre-scalar-product}. Within our
example we have (cf. also \refapp{btokstarll} and \cite{Lee:1992ih})
\begin{equation}
    |m| = \begin{cases}
        0\,, & k = 1,2,6\,,\\
        1\,, & k = 4,5,7,8\,,\\
        m\,, & k = 3,9
    \end{cases}\,.
\end{equation}
The angular observables $S_{k,j}$ defined as coefficients of this expansion in Legendre polynomials
have the merit of a well defined total angular momentum, and thus are physically discriminable.
As a consequence of the orthogonality of the Legendre polynomials, any mismodelling (or rather, lack of modelling of higher
partial-wave observables) \emph{does not affect} the method of moments as discussed in the previous section. To wit,
ignoring further (orthogonal) terms in the PDF cannot affect the mean vector $(\dots, S_k, \dots)$ nor its variance. \fred{yes!}\\

@@

In order to finally extract the angular observables from data, we use the \emph{measured raw moments}. Their MC estimator
$\lbrace \est{Q}_i\rbrace$ -- based on the \emph{detected events} $x^{(n)}$, $n=1,\dots,N$ -- reads
\begin{equation}
    \est{Q}_i \equiv R \frac{1}{N} \sum_n^N \tilde{f}_i(x^{(n)})\,.
\end{equation}
Here $R \equiv \int P(x) \eps(x)$ is an a priori unknown normalization that also occurs in the determination of the branching
ratio of the specific decay. We then obtain MC estimators of the angular observables via
\begin{equation}
    \label{eq:estS}
    \est{S}_i \equiv \sum_{i} \left(\hat{M}^{-1}\right)_{ij} \est{Q}_j\,.
\end{equation}
The precise value of $R$ depends on the a priori unknown angular observables $\lbrace S_i\rbrace$.
However, ratios and other suitable combinations of the estimators $\lbrace \est{S}_i\rbrace$ are independent
of $R$. Conversely, $R$ can be extracted from the self-consistency condition\footnote{This condition
is process dependent; see \refeq{recipe:lambdabtolambdall} and \refeq{recipe:btokstarll}.}
$\hat{S}_0 = \frac{1}{2}$. Since $R$ is relevant in the determination of the branching ratio, it is therefore useful
to carry out that determination and the extraction of the angular observables in a combined analysis.

\danny{
We note that the set $\lbrace \est{S}_k\rbrace$ as determined from \refeq{estS} does not fully correspond to the
set $\lbrace S_k\rbrace$ for an arbitrary $\eps$. Taking again the decay $B\to K\ell^+\ell^-$
as an example, we have $\dim S = 3$. Assuming an expansion of the detector acceptance $\eps$
in terms of Legendre polynomial up to order $L$, we obtain $\dim \est{Q} = \dim \est{S} = \dim S + L$.
The MC estimators then have the following structure:
\begin{equation}
    \lbrace \est{S}_k \rbrace = \lbrace \underbrace{\est{S}_0, \dots, \est{S}_{\dim S}}_\text{physical}, \underbrace{\est{S}_{\dim S + 1}, \dots, \est{S}_{\dim Q}}_\text{``superfluous''}\rbrace\,.
\end{equation}
The method is consistent as long as the MC estimators for the ``superfluous'' observables with indices $\dim S + 1$ to $\dim Q$
are compatible with zero. \footnote{This holds only for the physical model of uniangular decay distributions. For some decays, these superfluous observables
correspond to higher partial waves that have been suppressed in the physical model; see \refapp{btokstarll} for such a case.}
Since $L$ depends on the construction of the particle detector at hand, it remains for
the experimental collaborations to determine the maximum order of such an expansion.
}

@@

The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts --- reads \cite{Boeer:2014xx}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \sum_i S_i f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and
$N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
The index $i$ should be interpreted as a multi-index, $i \equiv (l_1, l_2, m)$,
where $0 \leq l_1 \leq 2$ and $0 \leq l_2 \leq 1$ denote the total angular momentum in the
dilepton and the $N\pi$ system, respectively, and $-1 \leq m \leq 1$
is the third component of either of the angular momenta.
Our choice of an orthonormal basis and its dual reads
\begin{equation}
\label{eq:lambdab:bases}
\begin{aligned}
    f_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
    & = \sqrt{\frac{(l_1 - |m|)!\,(l_2 - |m|)!}{(l_1 + |m|)!\,(l_2 + |m|)!}} p_{l_1}^{|m|}(\cos\theta_1) p_{l_2}^{|m|}(\cos\theta_2)\\
    & \times \begin{cases}
            \cos(|m|\theta_3) & m > 0\\
            \sin(|m|\theta_3) & m < 0\\
            1                 & m = 0
        \end{cases}\,,\\
    \tilde{f}_{l_1, l_2, m}(\cos\theta_1, \cos\theta_2, \theta_3)
    & = \frac{(2l_1 + 1)(2l_2 + 1)}{8\pi}\sqrt{\frac{(l_1 - m)!\,(l_2 - m)!}{(l_1 + m)!\,(l_2 + m)!}} p_{l_1}^m(\cos\theta_1) p_{l_2}^m(\cos\theta_2)\\
    & \times \begin{cases}
            2 \cos(|m|\theta_3) & m > 0\\
            2 \sin(|m|\theta_3) & m < 0\\
            1                   & m = 0
        \end{cases}\,.\\
\end{aligned}
\end{equation}
The correspondence between out choice of angular observables in the angular momentum basis, and the angular
observables as defined in reference \cite{Boeer:2014xx} reads
\begin{equation}
\begin{aligned}
    8\pi S_{0, 0,  0} & = 1\,,                                                             &
    8\pi S_{0, 1,  0} & = \frac{K_{2cc} + 2 K_{2ss}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
%
                      &                                                                    &
    8\pi S_{1, 1, -1} & = \frac{6 K_{4s}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
%
    8\pi S_{1, 0,  0} & = \frac{3 K_{1c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       &
    8\pi S_{1, 1,  0} & = \frac{3 K_{2c}}{\rmdx\Gamma/\rmdx{q^2}}\,,                       \\
%
                      &                                                                    &
    8\pi S_{1, 1, +1} & = \frac{6 K_{3s}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
%
                      &                                                                    &
    8\pi S_{2, 1, -1} & = \frac{2 \sqrt{3} K_{4sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,             \\
%
    8\pi S_{2, 0,  0} & = \frac{2(K_{1cc} - K_{1ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           &
    8\pi S_{2, 1,  0} & = \frac{2(K_{2cc} - K_{2ss})}{\rmdx\Gamma/\rmdx{q^2}}\,,           \\
%
                      &                                                                    &
    8\pi S_{2, 1, +1} & = \frac{2 \sqrt{3} K_{3sc}}{\rmdx\Gamma/\rmdx{q^2}}\,,
\end{aligned}
\end{equation}
where the decay width is
\begin{equation}
    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}\,.
\end{equation}

@@

For the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| < 1$.
The recipe's generating PDFs are therefore
\begin{equation}
    \label{eq:recipe:lambdabtolambdall}
    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}
        \begin{cases}
            \delta_{i,(0,0,0)}                  & j = (0, 0, 0)\\
            \delta_{i,(0,0,0)}  + \delta_{i,j}  & j \neq (0, 0, 0)
        \end{cases}
\end{equation}
where $j$ is now also a multi-index representing $j \equiv (\tilde l_1, \tilde l_2, \tilde m)$.

@@

    8\pi S_{1, 2, +1} & = \frac{4 \sqrt{3} J_{5}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,

@@

    8\pi S_{2, 1, -1} & = \frac{4 \sqrt{3} J_{8i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                            &
    8\pi S_{2, 2, -1} & = \frac{8 J_8}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                        \\

@@

    8\pi S_{2, 0,  0} & = \frac{4 (J_{2c} + 2 J_{2s})}{3\, \rmdx{\Gamma}/\rmdx{q^2}}\,,                    &

@@

    8\pi S_{2, 2,  0} & = \frac{8 (J_{2c} - J_{2s})}{3\, \rmdx{\Gamma}/\rmdx{q^2}}\,,                      \\
    8\pi S_{2, 1, +1} & = \frac{4\sqrt{3} J_{4i}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                             &
    8\pi S_{2, 2, +1} & = \frac{8 J_{4}}{\rmdx{\Gamma}/\rmdx{q^2}}\,,                                      \\
    8\pi S_{2, 2, +2} & = \frac{8 J_3}{\rmdx{\Gamma}/\rmdx{q^2}}                                           \\

@@

As before, for the purpose of unfolding acceptance effects as laid down in \refsec{systematics:acceptance}, it is instrumental
to know that $f_{0,0,0} \equiv 1$, and that $\max_{\cos\theta_1,\cos\theta_2,\phi} |f_{l_1, l_2, m}| \leq 1$.
The recipe's generating PDFs are therefore
\begin{equation}
    \label{eq:recipe:btokstarll}
    P(x|\lbrace S_i^{(j)}\rbrace)\,,\quad\text{with}\quad S_i^{(j)} = \frac{1}{8\pi}
        \begin{cases}
            \delta_{i,(0,0,0)}                  & j = (0, 0, 0)\\
            \delta_{i,(0,0,0)}  + \delta_{i,j}  & j \neq (0, 0, 0)
        \end{cases}
\end{equation}
where also $j$ is now a multi-index representing $j \sim (l_1, l_2, m)$.

\danny{
To conclude this section, we remind that the angular momentum $l_2$, associated with the angle $\theta$, is not bounded from above.
This has to be considered if partial waves beyond the P-wave are included in the analysis, see e.g. \cite{Das:2014sra}.
However, our choice of basis is well suited to these applications with $0 \leq l < \infty$. Note, that the
physical range of $m$ is not affected by higher partial waves.
}

@@

We propose the decomposition of $S$ in terms of the associated Legendre polynomials $p_{j}^{(m)}(\cos\theta)$, with total angular momentum $j$ and its third component $m=m_1 + m_2$.
\begin{equation}
    S(\theta) = \sum_j S_{j,m} p_{j}^{(m)}(\cos\theta)\,.
\end{equation}
This parametrization has two merits. First, we can immediately project out the angular observables $S_{j,m}$ by means of \refeq{legendre-scalar-product}:
\begin{equation}
    S_{j,m} = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} S(\theta) p_{j}^{(m)}(\cos\theta)\,.
\end{equation}
(Here and in the next step we may exchange the integral and the
series because each element of the series is a product of
polynomials on the compact support [-1,1], and thus each integral
is absolutely convergent).
Second, we can immediately express $S_{j,m}$ in terms of
the partial-wave amplitudes,
\begin{equation}
    \label{eq:partial-wave-observable-infinite}
    \begin{aligned}
        S_{j,m}
            & = \frac{1}{n_{j,m}} \int_{-1}^{+1} \rmdx{\cos\theta} p_{j}^{(m_1 + m_2)}(\cos\theta) \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{(l_1)} p_{l_1}^{(m_1)}(\cos\theta) A_{2}^{*(l_2)}p_{l_2}^{(m_2)}(\cos\theta)\right]\\
            & = \sum_{l_1,l_2=0}^\infty F\left[A_{1}^{(l_1)} A_{2}^{*(l_2)}\right] \frac{T_{l_1,l_2,j}^{(m_1,m_2)}}{n_{j,m}}\,,\qquad\text{with }m = m_1 + m_2\,.
    \end{aligned}
\end{equation}
